\documentclass[pagesize=auto, fontsize=12pt, parskip=half, DIV=11]{scrartcl}

\usepackage{fixltx2e}
\usepackage{etex}
\usepackage{xspace}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{microtype}
\usepackage{hyperref}

\newcommand*{\mail}[1]{\href{mailto:#1}{\texttt{#1}}}
\newcommand*{\pkg}[1]{\textsf{#1}}
\newcommand*{\env}[1]{\texttt{#1}}
\newsavebox{\tempbox}

\addtokomafont{title}{\rmfamily}

\title{The \pkg{overpic} package\thanks{This manual corresponds to \pkg{overpic}~v0.52, dated~1999/07/04.}}
\author{Rolf Niepraschk\thanks{\mail{niepraschk@ptb.de}}}
\date{1999/07/04}


\begin{document}

\maketitle

\noindent

\begin{quote}
  \footnotesize
  Copyright  1999 Rolf Niepraschk, \mail{niepraschk@ptb.de}\\
  This program can be redistributed and/or modified under the terms
  of the \LaTeX\ Project Public License Distributed from CTAN
  archives in directory \href{http://ctan.org/macros/latex/base/lppl.txt}{\texttt{macros/latex/base\slash lppl.txt}}; either
  version~1 of the License, or any later version.
\end{quote}

This small \LaTeX\ package defines the \env{overpic} environment which is
a combination between a \env{picture} environment and an \env{includegraphics}
command (defined in \pkg{graphicx}). The resulting \env{picture} environment has
the same dimension as the included \textsc{eps} graphic. Now it is easy possible
to put any \LaTeX\ output above the graphic on defined positions. A grid
to aid is also possible.

\begin{lrbox}{\tempbox}
  \begin{tabular}[b]{@{}l@{}}
    \texttt{opic-rel.tex} \\
    and                   \\
    \texttt{opic-abs.tex}
  \end{tabular}
\end{lrbox}

This directory contains the following files:
%
\begin{labeling}[\hspace{\labelsep}--]{\usebox{\tempbox}}
\item[\texttt{README}] This file.
\item[\texttt{README.de}] The same in german.
\item[\texttt{overpic.sty}] The definition of \env{overpic}. Required \env{graphicx.sty} and \env{epic.sty}.
\item[\usebox{\tempbox}] Two demos that shows all the features. You need the \textsc{eps} graphic file \texttt{golfer.ps}. This file is part of \textsc{ghostscript}'s  \texttt{examples} directory.
\end{labeling}
               
Please send comments and suggestions to \mail{niepraschk@ptb.de}.

Happy \TeX ing\ldots


\minisec{Changes:}

\begin{labeling}[\hspace{\labelsep}--]{v0.52, 1999/07/04}
  \item[v0.51, 1999/03/02] New (LPPL) license
  \item[v0.52, 1999/07/04] Correction of wrong height calculation (if $\mathrm{depth} \ne 0$)
\end{labeling}

\end{document}
